### 2015-05-08 fundamentals/fcsreqs.tex
reviewer 2:page 6: typing errors: ...facilitate... ...particular agent

Moreover, both technical and institutional aspects of the software development
practices employed by the \Cyclus community faciltate collaboration.
Technically, \Cyclus employs a set of tools commonly used collaborative
software development that reduce the effort required to comment on, test and
ultimately merge individual contributions into the main development path.
For many of the simulation platforms adopted by previous simulators, there were
technical obstacles that impeded this kind of collaboration.
Institutionally, \Cyclus invites all participants to propose, discuss and
provide input to the final decision making for all important changes.

@@

Modularity is a key enabler of extending the scope of fuel cycle analysis
within the \Cyclus framework.  Changes that are required to improve the
fidelity of modeling a paticular agent, or to introduce entirely new agents,
are narrowly confined and place no new requirements on the \Cyclus kernel.
Furthermore, there are very few assumptions or heuristics that would otherwise
restrict the algorithmic complexity that can be used to model the behavior of
such agents.

@@

\subsubsection{Discrete Facilities and Materials}

Many fuel cycle phenomena have aggregate system-level effects which can only be
captured by discrete material tracking \cite{huff_next_2010}.  \Cyclus
tracks materials as discrete objects. Some current fuel cycle simulation tools
such as \gls{COSI}
\cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
\gls{DESAE}
\cite{andrianova_desae_2008}, FAMILY21\cite{mccarthy_benchmark_2012},
\gls{GENIUS} version 1, \gls{GENIUS} version 2, and \gls{NFCSim} also possess the ability to
model discrete materials.

>>>>

Moreover, both technical and institutional aspects of the software development
practices employed by the \Cyclus community facilitate collaboration.
Technically, \Cyclus employs a set of tools commonly used collaborative
software development that reduce the effort required to comment on, test and
ultimately merge individual contributions into the main development path.
For many of the simulation platforms adopted by previous simulators, there were
technical obstacles that impeded this kind of collaboration.
Institutionally, \Cyclus invites all participants to propose, discuss and
provide input to the final decision making for all important changes.

@@

Modularity is a key enabler of extending the scope of fuel cycle analysis
within the \Cyclus framework.  Changes that are required to improve the
fidelity of modeling a particular agent, or to introduce entirely new agents,
are narrowly confined and place no new requirements on the \Cyclus kernel.
Furthermore, there are very few assumptions or heuristics that would otherwise
restrict the algorithmic complexity that can be used to model the behavior of
such agents.

@@

\subsubsection{Discrete Facilities and Materials}
Many fuel cycle phenomena have aggregate system-level effects which can only be
captured by discrete material tracking \cite{huff_next_2010}.  \Cyclus
tracks materials as discrete objects. Some current fuel cycle simulation tools
such as \gls{COSI}
\cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
\DIFdelbegin 
\DIFdel{\mbox{%DIFAUXCMD
\gls{DESAE} \cite{andrianova_desae_2008}
}%DIFAUXCMD
, }\DIFdelend FAMILY21\cite{mccarthy_benchmark_2012},
\gls{GENIUS} version 1, \gls{GENIUS} version 2, and \gls{NFCSim} also possess the ability to
model discrete materials.
